### 2019-05-28 doc/chapters/using_stainless.tex
Added Imperative features.

    def makeFoo(x: Int): Foo = new Foo {
      def bar: Int = x
    }
  \end{lstlisting}
  \item \textbf{Local classes}. The creation of local classes within a function are allowed.
\end{itemize}
\subsection{Predefined types}
\subsection{Imperative features}

>>>>

    def makeFoo(x: Int): Foo = new Foo {
      def bar: Int = x
    }
  \end{lstlisting}
  \item \textbf{Local classes}. 
  The creation of local classes within a function are allowed. \cite{Stainless:pure_scala}
  \item \textbf{Functional arrays} which use the operation that do not modify an array.
\end{itemize}

\subsection{Predefined types}

\subsection{Imperative features}

Stainless supports extensions to Pure Scala implemeting some imperative features.
They will be translated by Stainless into Pure Scala during a preprocessing phase.

The following imperative components are supported:

\begin{itemize}
  \item \textbf{Mutable variables} which can be declared with the keyword \textit{var}.
  Declaration of mutable variables is allowed only as a local variable within a function or in a case classe constuctor.
  \item  \textbf{While loops}. 
  Because besides main calculations in a loop the state of a loop counter changes at every iteration as a side effect, this kind of programming component does not belong to the functional paradigm and cannot be handled by solvers.
  Thus, Stainless generates automatically a postcondition with the negation of the loop condition as an argument. 
  Moreover, to make it stronger, the automatically generated postcondition can be customised with the keyword \textit{invariant}.
  An example of while loop implementation:
  \begin{lstlisting}[language=Scala]
    var res = 0
    var i = 0
    (while(i < 10) {
      res = res + i
      i = i + 1
    }) invariant(i >= 0 && res >= i)
  \end{lstlisting}
  \item \textbf{Arrays.} Stainless extends functional arrays allowing the reassignment of arrays elements.
  \item ...
\end{itemize}
